%%
%% The following code sets up the document formatting
%%

%this assumes that res_yy.sty is in some path
\documentstyle[hyperref, margin, centered]{res}

\hypersetup{backref,pdfpagemode=Full,backref}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.30in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\LARGE\bf}

\newcommand{\sectiontitle}{\sc}


%%
%% The following code defines some macros for terms which have raised font
%% (ie 4\fourth would result 4th with the 'th' raised (superscripted)
%%

\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\CSharp{{\rm C\raise.5ex\hbox{\small \#}}}
% 'st' 'nd' 'rd' 'th' superscripts for numbers
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}



%%
%% starting the actual document
%%

\begin{document}

%the name in big fonts at the top of resume
%this is left aligned
\name{Yiqing (Hannah) Xue}

%this is right aligned
\address{
yxue.me \textbar\ yx348@cornell.edu \textbar\ +1 (646) 245-7152
}

\begin{resume}

\vspace{25pt}

\section{\sectiontitle{About}}

Creative techie. Front-end and mobile developer. Self-taught designer. Visual Animal. 


\section{\sectiontitle{Education}}

\textbf{Cornell Tech}, New York, NY \hfill 2015--present \\
\textsl{M.S. in Information Systems, Connective Media} \\
Selected Courses: Startup Systems Design and Engineering, Applied Machine Learning, Master of Engineering Project, Independent Study (on Human-Computer Interaction).

\textbf{Peking University}, Beijing, China \hfill 2011--2015 \\ 
\textsl{B.S. in Computer Science with Honors and Scholarships}\\
Received 2014 Google China Anita Borg Scholarship (Only one in the department). \\
Selected Courses: Computer Networks (Honor Track), Operating Systems (Honor Track), Compilers, Web Software Technology, Human-Computer Interaction.

\textbf{Peking University}, Beijing, China \hfill 2012--2015 \\ 
\textsl{B.S. in Psychology}\\
Selected Courses: Social Psychology, Cognitive Psychology, Experimental Psychology.
% , Computer Architecture, Software Engineering

\begin{formatb}
  \employer{l}\dates{r}\\
  \title{l}\\
  % \location{l}
  \body\\
\end{formatb}


\section{\sectiontitle{Employment}}

\employer{\textbf{Baidu Research}, Beijing, China}
\title{\textsl{Research Intern} (OpenCV on Android)}
\dates{2015}
\begin{position}
Worked for the Human-Computer Interaction team at Baidu Institute of Deep-Learning. \\
Designed and built a high-fidelity prototype with natural user interfaces on tablets for a smart home hardware.
\end{position}

\employer{\textbf{Google}, Mountain View, CA}
\title{\textsl{Software Engineering Intern} (Google Web Toolkit, Android)}
\dates{2014}
\begin{position}
Implemented a new ads feature which enables advertisers to copy multiple ads asynchronously from existing ad groups directly from a table.\\
Worked with designer to prototype an Android app which scans a QR code on Google AdWords website and display multiple mobile ads on app.

\end{position}


%%
%% We use the same formatting for projects as for work experience
%% Shown below is the formatting used previously
%%
%%  \begin{formatb}
%%    \employer{l}\title{r}\\
%%    \location{l}\dates{r}\\
%%    \body\\
%%  \end{formatb}
%%
%% 
%%  Note that \location is now being used for non-location information
%%


\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\section{\sectiontitle{Projects}}

\employer{\textbf{Shake it} (mobile web application \textbar\ Python, Node.js, MongoDB)}
\dates{2015}
\begin{position}
Designed and developed a novel application where users could shake their phones to get coupons, which they could then star and share. The system is able to learn from user behaviors and perform better. 
Demo and paper available upon request.
\end{position}

\employer{\textbf{2D Barcode Redesign} (OpenCV on desktop and Android)}
\dates{2013-2014}
\begin{position}
Created and prototyped a redesign of scalable 2D barcode for wireless visual communication. Collaborated with Microsoft Research Asia and Yale University. Paper accepted by ACM MobiCom 2014 (Acceptance Rate 16.4\%).
\end{position}

\employer{\textbf{FYI: Find Your Instructor} (web application \textbar\ D3.js, Node.js, MongoDB)}
\dates{2014}
\begin{position}
The website provides gathered information of US professors for undergraduates who aim at further education. Designed and prototyped the entire website. Developed part of the front-end and back-end. 
\end{position}

% \employer{\textbf{Co.found} (mobile web application \textbar\ AngularJS, Node.js, MongoDB)}
% \dates{2014}
% \begin{position}
% \textsl{\href{https://co-found.herokuapp.com}{co-found.herokuapp.com}}\\
% Cofounder networking platform for Stanford community. UI+UX design and front-end dev.
% % Went through the entire design process of ideation, user study, rapid prototyping, user testing, etc.
% \end{position}

% \employer{\textbf{Visualization of Beijing Air Pollution} (visualization \textbar\ D3.js)}
% \dates{2012}
% \begin{position}
% \textsl{\href{http://scottcheng.github.com/bj-air-vis}{scottcheng.github.com/bj-air-vis}}\\
% Interactive visualization illustrating Beijing air pollution in time and space.
% \end{position}

\section{\sectiontitle{Skills}}
Java (Android), JavaScript, Python, \Cplusplus, HTML5, CSS3, Git.\\
UI+UX design.

\section{\sectiontitle{Interests}}
Graphic design, illustrating, fashion (Spent a summer at Parsons learning fashion). \\
Indie music. Tai-chi (Certified National Athlete).

\end{resume}
\end{document}
